Internal models of type theory and internal higher categories for the Univalent Foundations

### 2014-06-03 article-models-ttderived.tex
added ref to sec:fhom

Because composition is proven to be associative, we can draw diagrams involving
families and morphisms between them in a context $\Gamma$, just as is usual in
category theory and the order in which the morphisms are composed has no
relevance. We can also speak about pullback diagrams, with universality in a
judgmental sense.

@@

\subsection{Family morphisms}
In this section we are going to develop dependent morphisms and analyze various
sorts of composition. The notion of family morphism is the notion of `a 
morphism over a context morphism'. When we have established all the associativity
and interchange laws for all the compositions that come with the theory of
family morphisms, we will also be able to consider \emph{family diagrams}. Those
are graphical displays of situations in the theory of contexts, families and
terms, but unlike diagrams in category theory they can contain families (which
are strictly speaking not morphisms) and terms (which can be seen as morphisms,
but not in the way we're about to display them).

>>>>

Because composition is proven to be associative, we can draw diagrams involving
families and morphisms between them in a context $\Gamma$, just as is usual in
category theory and the order in which the morphisms are composed has no
relevance. We can also speak about pullback diagrams, with universality in a
judgmental sense. In \autoref{sec:fhom} we will introduce a more general kind
of diagrams which may also include families and `morphisms over morphisms'.

@@

\subsection{Family morphisms}\label{sec:fhom}
In this section we are going to develop dependent morphisms and analyze various
sorts of composition. The notion of family morphism is the notion of `a 
morphism over a context morphism'. When we have established all the associativity
and interchange laws for all the compositions that come with the theory of
family morphisms, we will also be able to consider \emph{family diagrams}. Those
are graphical displays of situations in the theory of contexts, families and
terms, but unlike diagrams in category theory they can contain families (which
are strictly speaking not morphisms) and terms (which can be seen as morphisms,
but not in the way we're about to display them).
